Cross-validation of regression models: mixed model examples (edited v3)

### 2024-09-14 scratch/JSS-submission/Revision-1/Fox-Monette-cv-package.Rmd
Divide section in JSS paper on other software into R and SAS/Stata/Python

@@

>>>>

In this section with briefly compare the \code{cv} package to other packages in \proglang{R} that support cross-validation, and then even more briefly consider facilities for cross-validation in other commonly used statistical software, \proglang{SAS}, \proglang{Stata}, and \proglang{Python}.

## Other R software

@@

## Other statistical software: SAS, Stata, and Python
